hormones

### 2019-10-08 analysis/07_hormones.Rmd
now with hormones

```{r prolactin-all}
prolactin %>%
  select(treatment, `Prolactin ng/mL`, Sex, study) %>% drop_na() %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(title = "Ciruclating prolactin levels",
       subtitle = "During characteristic parental care stages and following manipulation")
```

>>>>

```{r wranglesteroids}
PETC <- read_excel("../results/parental_care_hormone_RIA_data_master.xlsx", sheet = 2)

PETC <- PETC %>% select(stage, sex, hormone, plasma_conc)  %>%
                filter(stage %in% combolevels)  %>%
                droplevels()
PETC$stage <- factor(PETC$stage)
levels(PETC$stage)

PETC <- PETC %>%
    mutate(sex = fct_recode(sex,
                            "female" = "f",
                            "male" = "m"),
           study = fct_collapse(stage,
                                 characterization = charlevels,
                                 manipulation = maniplevels))
PETC$treatment <- factor(PETC$stage, levels = combolevels)

```{r prolactin}
prolactin %>%
  select(treatment, `Prolactin ng/mL`, Sex, study) %>% drop_na() %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Prolactin (ng/mL)")
```

```{r testosterone}

PETC %>% 
  filter(hormone == "testosterone", sex == "male")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Testosterone") +
  scale_fill_manual(values = c("#00BFC4"))
```

```{r estradiol}
PETC %>% 
  filter(hormone == "estradiol", sex == "female")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Estradiol (ng/mL)")

```{r progesterone}
PETC %>% 
  filter(hormone == "progesterone")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Progesterone (ng/mL)") +
  ylim(c(0,6))

```{r cort}

PETC %>% 
  filter(hormone == "cort")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Corticosterone (ng/mL)") +
  ylim(c(0,10))
